%-------------
% Research-Oriented CV (2-page friendly)
% Author : Sizhe (John) Zhang
% License: MIT
%------------

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear header/footer
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------
% Custom commands
\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}
\newcommand{\resumeItemWithoutTitle}[1]{\item\small{{#1\vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-0pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%-----HEADING---------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Sizhe (John) Zhang}} & Email: \href{mailto:sizhe@wustl.edu}{sizhe@wustl.edu} \\
  Mobile: +1 (314) 978-5700 & Website: \href{https://github.com/novaz03}{https://github.com/novaz03} \\ & GitHub Page: \href{https://github.com/novaz03}{https://github.com/novaz03}
  \multicolumn{2}{l}{} \\
\end{tabular*}

%------RESEARCH INTERESTS---------
\section{Research Interests}
\resumeSubHeadingListStart
  \resumeItemWithoutTitle{\textbf{Statistical Machine Learning:} robust/OO\!D generalization, uncertainty quantification, distribution shift, causal inference.}
  \resumeItemWithoutTitle{\textbf{Scientific ML \& Geospatial AI:} spatio-temporal statistics, mobility modeling under extremes, physics-/principle-informed learning.}
  \resumeItemWithoutTitle{\textbf{Optimization \& Computation:} large-scale training/evaluation, HPC/parallel computing (Slurm, Apptainer), numerical methods for AI.}
  \resumeItemWithoutTitle{\textbf{Reasoning \& LLMs:} data quality and evaluation for theorem proving/chain-of-thought; hybrid probabilistic–neural methods.}
\resumeSubHeadingListEnd

%------EDUCATION---------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Washington University in St.\ Louis (WashU)}{St.\ Louis, MO}
    {A.M.\ in Statistics \;(\emph{GPA 3.95/4.00})}{Aug 2023 -- Dec 2024}
  \resumeItemListStart
    \resumeItemWithoutTitle{\emph{Selected coursework:} Theory of Statistics, Nonparametric Estimation, Advanced Machine Learning, Linear Models, Mathematical Foundations of Big Data.}
  \resumeItemListEnd

  \resumeSubheading
    {University of Cambridge}{Cambridge, UK}
    {B.A.\ (Hons) in Natural Sciences}{Sep 2020 -- Jun 2023}
  \resumeItemListStart
    \resumeItemWithoutTitle{\emph{Selected coursework:} Statistics, Linear Algebra, Group Theory, Quantum Mechanics, Electromagnetism, Condensed Matter Physics, Special Relativity.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%------PUBLICATIONS & MANUSCRIPTS (do not fabricate; replace placeholders)---------
\section{Publications \& Manuscripts}
\resumeSubHeadingListStart
  \resumeItemWithoutTitle{\textbf{Manuscripts submitted (details on request):} spatial statistics and scientific ML projects on (i) multimodal human mobility under extreme weather and (ii) clinical driving behavior in preclinical Alzheimer's disease.}
  % Example (replace with real citations if available):
  % \resumeItemWithoutTitle{Zhang, S.\ et al.\ (2025). \emph{Title of the mobility manuscript}. Under review.}
  % \resumeItemWithoutTitle{Zhang, S.\ et al.\ (2025). \emph{Title of the clinical AD manuscript}. Under review.}
\resumeSubHeadingListEnd

%------RESEARCH EXPERIENCE---------
\section{Research Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Geospatial Hazard Research Team (Prof.\ Nan Lin; collaborators across WashU)}{St.\ Louis, MO}
    {Graduate Researcher}{May 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Geospatial AI for Disaster Response}{Constructed high-resolution, hexagon-based spatio-temporal mobility datasets; integrated POI semantics and graph embeddings to study pre-/post-event behavioral change under hurricanes.}
    \resumeItem{Methods}{Uncertainty-aware clustering and causal analyses for distribution shift; scalable ETL and quality control pipelines for heterogeneous mobility/POI/socioeconomic data.}
    \resumeItem{Impact}{Produced decision-support summaries for evacuation vs.\ shelter-in-place patterns and critical infrastructure access; documented reproducible pipelines for multi-terabyte data.}
    \resumeItem{Stack}{Python (GeoPandas, PyTorch, scikit-learn), PostGIS, QGIS; HPC (Slurm arrays, Apptainer/Singularity)}
  \resumeItemListEnd

  \resumeSubheading
    {DRIVES Project (Clinical AI; PI: Dr.\ Ganesh M.\ Babulal)}{St.\ Louis, MO}
    {Researcher}{2025 -- Present}
  \resumeItemListStart
    \resumeItem{Clinical Time-Series Modeling}{Analyzed naturalistic driving data to quantify effects of preclinical Alzheimer's disease on mobility/risk; built robust feature pipelines with rigorous validation.}

  \resumeItemListEnd

  \resumeSubheading
    {Automated Theorem Proving \& Reasoning AI}{St.\ Louis, MO}
    {Graduate Research Assistant}{Feb 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Whole-Proof Generation}{Designed proof-tree data structures and intermediate verification to stabilize long-chain reasoning; established metrics for data completeness/consistency.}
    \resumeItem{LLM Data Quality}{Developed versioned pipelines for reasoning datasets (Lean4) with anomaly detection; documented best practices to reduce leakage and spurious correlations.}
    \resumeItem{Stack}{Python, Lean4, Git/DVC; evaluation harnesses for chain-of-thought.}
  \resumeItemListEnd

  \resumeSubheading
    {Aviation Impact Accelerator (Business \& Policy Group)}{Cambridge, UK}
    {Undergraduate Researcher}{Jun 2022 -- Sep 2022}
  \resumeItemListStart
    \resumeItem{Techno-Economic Modeling}{Integrated fuel/material flow and capital cost data; built regression-based operating cost models and scenario tools for decision support.}
    \resumeItem{Stack}{MATLAB, R, interactive reporting in Excel/Markdown.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%------RESEARCH-RELEVANT PROFESSIONAL APPOINTMENTS---------
\section{Research-Adjacent Roles}
\resumeSubHeadingListStart
\resumeSubheading
  {Operations \& Systems Specialist I (Radiology)}{St.\ Louis, MO}
  {Washington University School of Medicine}{Apr 2025 -- Present}
\resumeItemListStart
  \resumeItem{AI Model Development \& Deployment}{
    Co-developed LLM components for patient-facing clinical workflows (retrieval-augmented generation, prompt schemas, safety filters); implemented PEFT/LoRA training pipelines and lightweight adapters for domain adaptation; stood up evaluation harnesses for factuality/hallucination, uncertainty proxies, and regression tests against reference corpora.}
  \resumeItem{Large-Scale Training \& HPC}{
    Orchestrated distributed jobs on Slurm (arrays, GPU/CPU mix), profiled throughput and memory (mixed precision, gradient accumulation), and containerized stacks (Docker/Apptainer) with \texttt{lmod} modules for reproducible builds. }

\resumeItemListEnd



  \resumeSubheading
    {Teaching Assistant}{St.\ Louis, MO}
    {Washington University in St.\ Louis}{Jan 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Courses}{Python for Data Science, Stochastic Processes, Mathematical Foundations of Big Data; led tutorials, office hours, and assessment design.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%------SELECTED PROJECTS (brief, research-facing)---------
\section{Selected Projects}
\resumeSubHeadingListStart
  \resumeItem{Mobility Graph Embeddings under Extreme Events}{Node2Vec/LLM-derived POI embeddings on EPSG:5070 hex grids; clustering trajectories over 143-hour windows; evaluation under distribution shift.}
  \resumeItem{Automated Theorem Proving \& Reasoning AI}{Leakage audits, adversarial paraphrases, influence-function diagnostics, and proof-tree data structures for long-chain reasoning datasets (Lean4); versioned pipelines and evaluation harnesses for chain-of-thought stability.}
  \resumeItem{Reasoning Dataset Curation}{Leakage audits, adversarial paraphrases, and influence-function diagnostics for long-chain proof corpora.}
  
  \resumeItem{AIGlucose}{
    Led the \href{https://github.com/novaz03/AIGlucose}{AIGlucose} project: an evaluation-first toolkit for plain-language, evidence-linked explanations of glucose patterns. Integrated domain-specific retrieval, span-level evidence display, and a factuality checker.}
\resumeSubHeadingListEnd

%------TECHNICAL & METHODS---------
\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeItem{Languages}{Python, R, MATLAB, C++, SQL, Bash; (working) Lean4.}
  \resumeItem{ML/Stats}{PyTorch, scikit-learn, XGBoost; Bayesian modeling, conformal prediction (UQ), causal inference, robust estimation, nonparametrics, time-series, geospatial statistics.}
  \resumeItem{Geospatial}{GeoPandas, Shapely, Rasterio, PostGIS, QGIS; EPSG:5070 workflows; hex tiling and network construction.}
  \resumeItem{HPC/Systems}{Slurm job arrays, Apptainer/Singularity, CUDA-capable nodes, BeeGFS/CephFS; SSH tunneling, advisory file locks; profiling/monitoring at scale.}
  \resumeItem{Data/DevOps}{Git/GitHub, DVC, MLflow/Weights\&Biases (exp.\ tracking), Make/Snakemake; testing \& CI basics.}
  \resumeItem{Reproducibility}{Containerized pipelines, metadata/versioning, structured experiment logs, documentation and onboarding guides.}
\resumeSubHeadingListEnd

%------SERVICE & OUTREACH (optional)---------
% \section{Service \& Outreach}
% \resumeSubHeadingListStart
%   \resumeItemWithoutTitle{Open-source contributions (selected): ...}
%   \resumeItemWithoutTitle{Mentoring junior researchers/peers in HPC usage and experiment design.}
% \resumeSubHeadingListEnd


\end{document}
